\section*{Acknowledgement}
\addcontentsline{toc}{section}{Acknowledgement}

The internship opportunity I had with National Institute od Informatics (NII) was a great chance for learning and professional development. Therefore, I consider myself as a very lucky individual as I was provided with an opportunity to be a part of it. I am also grateful for having a chance to meet so many wonderful people and professionals who led me though this internship period.

I express my deepest thanks to Dr. Pr. Katsumi Inoue, my team leader and my supervisor for taking part in useful decision \& giving necessary advices and guidance and arranged all facilities to make life easier. I choose this moment to acknowledge his contribution gratefully.

Bearing in mind previous I am using this opportunity to express my deepest gratitude and special thanks to my Ph.D. supervisor Ass. Pr. Morgan Magnin who in spite of being extraordinarily busy with his duties, took time out to hear, guide and keep me on the correct path and allowing me to carry out my researches at their esteemed organization and extending during the training.

It is my radiant sentiment to place on record my best regards, deepest sense of gratitude to my supervisor Dr. P. Olivier Roux at France for his careful and precious guidance which were extremely valuable for my study both theoretically and practically. Also I want to thank him and thank Ass. P Morgan Magnin for their effort to allow me to do this interesting internship.

I also would like to thank all the people that worked in the office of NII in Tokyo. With their
patience and openness they created an enjoyable working environment.
Furthermore I want to thank all the scientist and students, with whom I did the fieldwork. We
experienced great things together.

I perceive as this opportunity as a big milestone in my career development. I will strive to use gained skills and knowledge in the best possible way, and I will continue to work on their improvement, in order to attain desired career objectives. Hope to continue cooperation with all of you in the future.

