\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

Almost the models of biological networks are not robust and need some times to be revised and adapted to the new observations. A system maintains its functions against internal and external perturbations, leading to topological changes in the network with varying delays. To understand the resilient behaviour of biological networks, we propose novel methods. First we propose an approach to model a time-dependent asynchronous and non-deterministic networks through Process Hitting (PH) framework which is a new framework particularly suitable to model biological regulatory networks. Second we have developed a novel network completion algorithm for time-varying networks to analyse its behavior based on the framework of network completion. This completion aims to make the minimum amount of modifications to a given network so that the resulting network is most consistent with the observed data.
We demonstrate the effectiveness of our proposed methods through computational experiments using synthetic gene expression data of the circadien clock network modeled through PH.  The results indicate that our methods exhibit good performance in terms of completing and inferring gene association networks with time-varying structures.

%This paper studies problems of completing a given Boolean network (Boolean circuit) so that the input/output behavior is consis- tent with given examples, where we only consider acyclic networks. These problems arise in the study of inference of signaling networks using re- porter proteins. We prove that these problems are


% We verify this by simulations of a simple model for interactions among cells.

%Circadian rhythms are certain periodic behaviours exhibited by living organism at different levels, including cellular and system-wide scales. Recent studies have found that the circa- dian rhythms of several peripheral organs in mammals, such as the liver, are able to entrain their clocks to received signals independent of other system level clocks, in particular when responding to signals generated during feeding. 
%The properties of the model show that the circadian system itself is strongly robust, and is able to continually evolve

%Asymptotic behavior is often of particular interest when an- alyzing asynchronous Boolean networks representing biological systems such as signal transduction or gene regulatory networks.

%In this paper, we propose a novel optimization-based method for computing all maximal symbolic steady states and motivate their use. In particular, we add a new result yielding a lower bound for the number of cyclic attractors and illustrate the methods with a short study of a MAPK pathway model.
